Automatically proving equivalence by type-safe reflection

### 2016-01-19 paper-JFP-DTP/content/6-discussion.tex
Finished

In terms of performances, our implementation is fast enough for providing answers in a decent amont of time --usually a few seconds--. The automatic proof of the lemma $adc\_lemma\_2$ (presented in section~\ref{sect:motivatingExample} and proven automatically in section ~\ref{sect:results}) is constantly generated and printed in less than 8 seconds on a dual core i5 processor @ 2.4ghz and is therefore perfectly usable, even for this kind of moderate size goals that come from a real application. Knowing that the display of the proof takes most of the time, it would be interesting to evaluate precisely the time needed for its generation only, without outputting the result. However, we suspect that our implementation will be slower than Coq, because they've used a more efficient representation of normalised polynomials. It might be possible that we've traded some efficiency against some simplicity and compositionality.

@@

	\subsection {Conclusion and related work}

XXX

>>>>

In terms of performances, our implementation is fast enough for providing answers in a decent amont of time --usually a few seconds--. For example, the automatic proof of the lemma $adc\_lemma\_2$ (presented in section~\ref{sect:motivatingExample} and proven automatically in section ~\ref{sect:results}) is constantly generated and printed in less than 8 seconds on a dual core i5 processor @ 2.4ghz and is therefore perfectly usable, even for this kind of moderate to large size proofs that come from a real application. Knowing that the display of the proof takes most of the time, it would be interesting to evaluate precisely the time needed for its generation only, without outputting the result. However, we suspect that our implementation will be slower than Coq, because they've used a more efficient representation of normalised polynomials. It might be possible that we've traded some efficiency against some simplicity and compositionality of the various provers.

@@

	\subsection {Conclusion and futur work}

This paper has shown that type-safe reflection techniques can enable to manipulate proofs terms easily. We've been able to build an entire hierarchy of tactics for algebraic structures precisely because the construction of the proof terms has been greatly facilitated by the use this technique. We end up with a hierarchy of reflexive tactics for proving equivalence in semigroups, monoids, commutative monoids, groups, commutative groups, pre semi-ring, semi-ring, rings and commutative rings, without having had to repeat our efforts.

It is even possible to extend a prover in order to build a dedicated one for a specific structure that isn't exactly a well known algebraic structure. We are at the moment investigating the extention of the pre semi-ring prover in order to build a prover for regular expressions. Regular expressions have a union of language playing the role of $+$ (which is associative, commutative, and which has a neutral element $\emptyset$) and a product of language playing the role of $*$, which is associative, distributive over the union, and which admits the empty word $\epsilon$ for neutral element. However, it has also a Kleene $star$ construction and a few properties about it. We currently aim to extend the pre semi-ring prover in order to build a prover for regular expression. Such a prover would be useful for doing formally verified transformations of regular grammars and final states machines for free, which could go up to a formally verified (for free!) parser generator for regular languages.
